Notes

### 2024-08-29 article.qmd
update: tables in manuscript

First, the missions, instruments and data used are listed. Then, we brieﬂy describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase. Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.

@@

Overview. **a,** Juno orbit during its cruise phase (2011-206). **b,** Difference of heliographic longitude of Juno and 1-AU missions. **c,** monthly and smoothed sunspot number. **d-g,** Near-Earth (OMNI) and STEREO-A solar wind plasma density and speed.

@@

Furthermore, an analysis of @fig-overview reveals the significance of the heliographic longitudinal difference between the Juno mission and Near-Earth missions (such as Wind and ARTEMIS) as well as STEREO-A missions. This longitudinal discrepancy ensures comprehensive coverage of the plasma en route to Juno. Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa. This relationship facilitates an extensive observation network for the plasma traveling towards Juno.

@@

@@

# Archived Figures

::: {#fig-current layout-nrow="1"}
![](figures/new/current/current_k_r_dist)

![](figures/new/current/current_k_N1_r_dist)

**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
:::

::: {#fig-thickness layout-nrow="1"}
![](figures/new/thickness/thickness_k_fit_r_dist)

![](figures/new/thickness/thickness_k_fit_N1_r_dist)

**a,** Thickness of IDs as a function of the radial distance from the Sun. **b,** Thickness of IDs normalized to the ion inertial length as a function of the radial distance from the Sun. 
:::

![](figures/l_j_fit_taus)

![](figures/l_j_fit_taus_xscale_log)

::: {.column-screen-inset layout-nrow="1"}
![](figures/thickness/thickness_k_dist)

![](figures/thickness/thickness_k_N1_dist)

![](figures/thickness/thickness_k_N1_r_dist)
:::

::: {.column-screen-inset layout-nrow="1"}

![](figures/current/current_k_dist)

![](figures/current/current_k_N1_dist)

>>>>

First, the missions, instruments and data used are listed. Then, we briefly describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase. Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.

@@

Overview. **a,** Juno orbit during its cruise phase (2011-2016). **b,** Difference of heliographic longitude of Juno and 1-AU missions. **c,** monthly and smoothed sunspot number. **d-g,** Near-Earth (OMNI) and STEREO-A solar wind plasma density and speed.

@@

Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission. Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa. This longitudinal discrepancy between Earth and STEREO-A ensures comprehensive coverage of the plasma en route to Juno.

@@

| Mission             | δt(B)    | δt(plasma) |
|---------------------|----------|------------|
| Juno                | 1 Hz     | 1 hour     |
| ARTEMIS             | 5 Hz     | 0.25 Hz    |
| WIND                | 11 Hz    | 1 Hz       |
| STEREO              | 8 Hz     | 1 min      |

@@

### 2024-08-29 notes.qmd
update: tables in manuscript

## Updates

@@

## Infos

```{python}
# | label: tbl-missions
# | tbl-cap: Missions info
import yaml
import polars as pl
from functools import reduce
from great_tables import GT

with open("data/info.yml", "r") as file:
    data = yaml.safe_load(file)

# Recursive function to find magnetometers
def find_instrument(instruments, ins_type):
    instrument = {}
    for key, value in instruments.items():
        if value.get("type") == ins_type:
            instrument = value
        elif "instruments" in value:
            instrument = find_instrument(value["instruments"], ins_type)
    return instrument

def parse_yaml(data, info, ins_type=None):
    rows = []

    for mission, details in data["missions"].items():
        if ins_type is None:
            rows.append([mission, details.get(info)])
            continue
        instruments = details.get("instruments", {})
        instrument = find_instrument(instruments, ins_type)
        rows.append([mission, instrument.get(info)])

    return pl.DataFrame(rows, schema=["Mission", info])

# Define the merge function
def merge_dfs(left: pl.DataFrame, right, on="Mission", how="outer_coalesce"):
    return left.join(right, on=on, how=how)

# Parse and display the table
df_mag = parse_yaml(data, "time_resolutions", "magnetometer").rename(
    {"time_resolutions": "δt(B)"}
)
df_plasma = parse_yaml(data, "time_resolutions", "plasma").rename(
    {"time_resolutions": "δt(plasma)"}
)
df_r = parse_yaml(data, "radial_coverage")
df_time = parse_yaml(data, "launch_date")
df_link = parse_yaml(data, "website")

df_list = [df_mag, df_plasma, df_r, df_time, df_link]  # Replace with your DataFrames

df_merged = reduce(merge_dfs, df_list).with_columns(pl.col("website").list.join(", "))

GT(df_merged.to_pandas()).fmt_markdown("website").cols_label(
    radial_coverage="Radial coverage",
    launch_date="Launch date",
)
```

>>>>

# Updates

@@

# Archived Figures

::: {#fig-current layout-nrow="1"}
![](figures/new/current/current_k_r_dist)

**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
:::

::: {#fig-thickness layout-nrow="1"}
![](figures/new/thickness/thickness_k_fit_r_dist)

**a,** Thickness of IDs as a function of the radial distance from the Sun. **b,** Thickness of IDs normalized to the ion inertial length as a function of the radial distance from the Sun. 
:::

![](figures/l_j_fit_taus)

![](figures/l_j_fit_taus_xscale_log)

::: {.column-screen-inset layout-nrow="1"}
![](figures/thickness/thickness_k_dist)

![](figures/thickness/thickness_k_N1_dist)

![](figures/thickness/thickness_k_N1_r_dist)
:::

::: {.column-screen-inset layout-nrow="1"}

![](figures/current/current_k_dist)

![](figures/current/current_k_N1_dist)
